A pipeline to analyse time-course gene expression data

### 2019-08-09 scripts/manuscript.Rmd
remove changes that require new plot_centroids

```{r fig.height=6, fig.width=6}
top_DE_genes_pval = names(sort(pvalue)[1:10])
plot_genes(data[top_DE_genes_pval, ], splines_model,
    colors=ann_colors$Group, smooth=TRUE,
    mar=c(1.5,2.5,2,0.1), legendArgs=list(title="Treatment"))
```

@@

```{r fig.height=6, fig.width=6}
top_DE_genes_lfc = names(
    sort(abs(lfc_epicon),
	 decreasing=TRUE)[1:10])
plot_genes(data[top_DE_genes_lfc, ], splines_model,
    colors=ann_colors$Group, smooth=TRUE,
    mar=c(1.5,2.5,2,0.1), legendArgs=list(title="Treatment"))

@@

```{r fig.height=6, fig.width=6}
plot_centroids(kmeans_clusters$centroids, splines_model,
    colors=ann_colors$Group,
    smooth=TRUE,legend=TRUE,
    legendArgs=list(title="Treatment",cex=2))
```

>>>>

```{r fig.height=6, fig.width=6}
top_DE_genes_pval = names(sort(pvalue)[1:10])
plot_genes(data[top_DE_genes_pval, ], splines_model,
    colors=ann_colors$Group, smooth=TRUE,
    mar=c(1.5,2.5,2,0.1))
```

@@

```{r fig.height=6, fig.width=6}
top_DE_genes_lfc = names(
    sort(abs(lfc_epicon),
	 decreasing=TRUE)[1:10])
plot_genes(data[top_DE_genes_lfc, ], splines_model,
    colors=ann_colors$Group, smooth=TRUE,
    mar=c(1.5,2.5,2,0.1))

@@

```{r fig.height=6, fig.width=6}
plot_centroids(kmeans_clusters$centroids, splines_model,
    colors=ann_colors$Group,
    smooth=TRUE)
```
